### 2017-10-06 Gruba/06-perf.tex

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{figures/Interests}
\caption{Testing Results with Various $\alpha$ \tbc{}}
\label{fig:fe}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=.96\linewidth]{figures/clustering}
\caption{Silhouette Coefficient Values for Various Cluster Numbers over Different Testing Datasets \tbc{}}
\label{fig:uc}
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure[Precision]{
    \label{fig:10-a} 
    \includegraphics[width=0.4\textwidth]{figures/precision.eps}}
  \hspace{1in}
  \subfigure[Recall]{
    \label{fig:10-b} 
    \includegraphics[width=0.4\textwidth]{figures/recall.eps}}
  \hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:10-c} 
    \includegraphics[width=0.4\textwidth]{figures/F-Measure.eps}}
  \caption{Performance of \sys{} Versus LRC-BQ \tbc{}}
  \label{fig:10} 
\end{figure}

@@

\begin{figure}
  \centering
  \subfigure[Precision]{
    \label{fig:11-a} 
    \includegraphics[width=0.4\textwidth]{figures/precisionofdifferentfeatures.eps}}
  \hspace{1in}
  \subfigure[Recall]{
    \label{fig:11-b} 
    \includegraphics[width=0.4\textwidth]{figures/recallofdifferentfeatures.eps}}
  \hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:11-c} 
    \includegraphics[width=0.4\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
  \caption{\sys{} Performance of Using Various Data Items for Modeling \tbc{}}
  \label{fig:11}
\end{figure}

>>>>

\begin{figure}[!htb]
\centering
\includegraphics[width=.7\linewidth]{figures/Interests}
\caption{Testing Results with Various $\alpha$.}
\label{fig:fe}
\end{figure}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=.7\linewidth]{figures/clustering}
\caption{Silhouette Coefficient Values for Various Cluster Numbers over Different Testing Datasets.}
\label{fig:uc}
\end{figure}

@@

\begin{figure*}
  \centering
  \subfigure[Precision]{
    \label{fig:10-a}
    \includegraphics[width=0.3\textwidth]{figures/precision.eps}}
  %\hspace{1in}
  \subfigure[Recall]{
    \label{fig:10-b}
    \includegraphics[width=0.3\textwidth]{figures/recall.eps}}
  %\hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:10-c}
    \includegraphics[width=0.3\textwidth]{figures/F-Measure.eps}}
  \caption{Performance of \sys{} Versus LRC-BQ.}
  \label{fig:10}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[Precision]{
    \label{fig:11-a}
    \includegraphics[width=0.3\textwidth]{figures/precisionofdifferentfeatures.eps}}
  %\hspace{1in}
  \subfigure[Recall]{
    \label{fig:11-b}
    \includegraphics[width=0.3\textwidth]{figures/recallofdifferentfeatures.eps}}
  %\hspace{1in}
  \subfigure[$F_1$ Score]{
    \label{fig:11-c}
    \includegraphics[width=0.3\textwidth]{figures/fmeasureofdifferentfeatures.eps}}
  \caption{\sys{} Performance of Using Various Data Items for Modeling.}
  \label{fig:11}
\end{figure*}
